Artificial ecosystem selection to deduce the mapping between microbial community structure and ecosystem function

### 2020-10-15 Manuscript/manuscript.Rmd
Update Makefile, remove old scripts, create new numbered scripts

---
title: Artificial ecosystem selection to deduce the mapping between microbial community structure and ecosystem function
author: "Andrew H. Morris and Brendan J. M. Bohannan"
output:
  html_document: default
  word_document:
    reference_docx: reference.docx
editor_options:
  chunk_output_type: inline
---

@@

her_fit <- lm(offspring ~ parental, data = heritability)
her_sum <- tidy(summary(her_fit))
her_aov <- tidy(anova(her_fit))

>>>>

---
title: Artificial ecosystem selection to deduce the mapping between microbial community structure and ecosystem function
author: "Andrew H. Morris and Brendan J. M. Bohannan"
output:
  word_document:
    reference_docx: reference.docx
editor_options:
  chunk_output_type: inline
---

@@

her_fit <- lm(offspring ~ parental, data = heritability)
her_sum <- tidy(her_fit)
her_aov <- tidy(anova(her_fit))
